Finalize dataset for *Phenotypic evolution is more constrained in simpler food webs*

### 2019-01-17 data/raw_data_management/finalize_manuscript_dataset.Rmd
moved to a new folder and changed file path

```{r Filter dataset}
gall_selection.df <- read_csv("data/raw_data_management/gall_selection_data.csv") %>%
  filter(phenology == "early", Location == "tree") %>%
  select(Treatment = Treatment.focus, 
         # unique identifying information at the plant- and gall-level
         Genotype, # plant genotype ID
         Plant_Position, # unique plant ID (also corresponds to position within the common garden experiment)
         Gall_Number, # unique multi-chambered gall ID
         Gall_Letter, # unique chamber ID within gall number
         # rename traits and add measurement units to variable
         chamber.diameter_mm = Gall_Height_mm, # chamber-level
         oviposition.preference_individuals.per.100.shoots = Density_per_100_shoots, # plant-level
         clutch.size_individuals = gall_individuals, # gall-level
         pupa, # successful pupation of larval Iteomyia salicisverruca
         egg.ptoid = platy, # reared egg parasitoid, Platygaster sp. from gall chamber
         larval.ptoid = ectos, # reared larval parasitoid (most of which were ectoparasitoids) from gall chamber
         early.larval.death = none.none) # early larval death = no larva or exit hole associated with gall chamber

>>>>

```{r Filter dataset}
gall_selection.df <- read_csv("gall_selection_data.csv") %>%
  filter(phenology == "early", Location == "tree") %>%
  select(Treatment = Treatment.focus, 
         # unique identifying information at the plant- and gall-level
         Genotype, # plant genotype ID
         Plant_Position, # unique plant ID (also corresponds to position within the common garden experiment)
         Gall_Number, # unique multi-chambered gall ID
         Gall_Letter, # unique chamber ID within gall number
         # rename traits and add measurement units to variable
         chamber.diameter_mm = Gall_Height_mm, # chamber-level
         oviposition.preference_individuals.per.100.shoots = Density_per_100_shoots, # plant-level
         clutch.size_individuals = gall_individuals, # gall-level
         pupa, # successful pupation of larval Iteomyia salicisverruca
         egg.ptoid = platy, # reared egg parasitoid, Platygaster sp. from gall chamber
         larval.ptoid = ectos, # reared larval parasitoid (most of which were ectoparasitoids) from gall chamber
         early.larval.death = none.none) # early larval death = no larva or exit hole associated with gall chamber
